Language-Based Security for Low-Level MPC

### 2024-08-22 csf25/lang.tex

A key technical distinction of the malicious setting is that it
typically incorporates ``abort''. Honest parties implement strategies
to detect rule-breaking-- aka \emph{cheating}-- by using, e.g.,
message authentication codes with semi-homomorphic properties as in
BDOZ/SPDZ \cite{10.1007/978-3-030-68869-1_3}. If cheating is detected,
the protocol is aborted. To model this, we extend $\minifed$ with an
\ttt{assert} command:
$$
    \begin{array}{rcl@{\hspace{2mm}}r}
      \prog &::=& \cdots \mid \assert{\be = \be}
    \end{array}
$$
and extend the range of memories with
$\bot$. Note that the adversary is free to ignore their own
assertions.
\begin{definition}
  We add assertions of the form $\elab{\assert{\phi(\be)}}{\cid}$ to the command
  syntax of $\minifed$, where $\phi$ is a decidable predicate on
  $\mathbb{F}_p$ and with operational semantics given in Figure
  \ref{fig-adversary}. We also extend the range of memories $\store$
  to $\mathbb{F}_p \cup \{ \bot \}$.
\end{definition}

>>>>

A key technical distinction of the malicious setting is that it
typically incorporates ``abort''. Honest parties implement strategies
to detect rule-breaking-- aka \emph{cheating}-- by using, e.g.,
message authentication codes with semi-homomorphic properties as in
BDOZ/SPDZ \cite{10.1007/978-3-030-68869-1_3}. If cheating is detected,
the protocol is aborted. To model this, we extend $\minifed$ with an
\ttt{assert} command:
$$
    \begin{array}{rcl@{\hspace{2mm}}r}
      \prog &::=& \cdots \mid \assert{\be = \be}
    \end{array}
$$

The big-step adversarial semantics relation $\aredx$ is then defined
in Figure \ref{fig-minicat-aredx} as a mapping from configurations to
$\stores$ or $\bot$.

As we will discuss, this form of asserting equality between expressions
is sufficient to capture MAC checking and support integrity in protocols.

### 2024-08-22 csf25/smt.tex
checkpoint

@@

We write $\eqs_1 \models \eqs_2$ iff every model of $E_1$ is a model of $E_2$. Note that
this relation is reflexive and transitive.

@@

\begin{mathpar}
  \toeq{\OT{\be_1}{\cid_1}{\be_2}{\be_3}{\cid_2}} =
  (\toeq{\elab{\be_1}{\cid_1}} \wedge \toeq{\elab{\be_3}{\cid_2}}) \vee
  (\neg\toeq{\elab{\be_1}{\cid_1}} \wedge \toeq{\elab{\be_2}{\cid_2}}) 
\end{mathpar}

>>>>

In previous work we have shown that the semantics of $\minicat$ in
$\mathbb{F}_2$ can be implemented with Datalog \cite{skalka-near-ppdp24}, which is
essentially a form of constraint programming. In this paper we extend
this idea to arbitrary prime fields by using a more general form of
SMT constraint programming, specifically Satisfiability Modulo Finite
Fields \cite{SMFF}. As we will show in subsequent sections, this
interpretation supports correctness guarantees, and also static type
analyses for enforcing confidentiality and integrity properties.

@@

\begin{mathpar}
  \store(\phi_1 \fplus \phi_2) = \cod{\store(\phi_1) \fplus \store(\phi_2)}

  \store(\phi_1 \ftimes \phi_2) = \cod{\store(\phi_1) \ftimes \store(\phi_2)}

  \store(\phi_1 \fminus \phi_2) = \cod{\store(\phi_1) \fminus \store(\phi_2)}
\end{mathpar}

\begin{definition}
  Given $\eqs$ of the form $\phi_1 \eop \phi_1' \wedge \cdots \wedge \phi_n \eop
  \phi_n'$ and $\store$, we say that $\store$ is a \emph{model} of
  $\eqs$, written $\store \models \eqs$, iff $\store(\phi_i) =
  \store(\phi_i')$ for all $1 \le i \le n$. We write $\eqs_1 \models
  \eqs_2$ iff  $\store \models E_1$ implies $\store \models
  E_2$ for all $\store$, and note this relation is reflexive and transitive.
\end{definition}

\begin{theorem}
  $\eqs \models \phi \eop \phi'$ iff $\eqs \wedge \phi \not\eop \phi'$ is
  not satisfiable.
\end{theorem}

@@

\begin{mathpar}
  \toeq{\elab{\OT{\be_1}{\cid_1}{\be_2}{\be_3}}{\cid_2}} =
  (\toeq{\elab{\be_1}{\cid_1}} \wedge \toeq{\elab{\be_3}{\cid_2}}) \vee
  (\neg\toeq{\elab{\be_1}{\cid_1}} \wedge \toeq{\elab{\be_2}{\cid_2}}) 
\end{mathpar}
